Who does big team science?

### 2023-04-20 manuscript_scopus.Rmd
finalizing pre-reg

---
title             : "Who does big team science?"
shorttitle        : "Big Team Science"
author: 
  - name          : "Erin M. Buchanan"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "326 Market St., Harrisburg, PA 17101"
    email         : "ebuchanan@harrisburgu.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Data curation
      - Formal Analysis
      - Methodology
      - Project administration
      - Visualization
      - Writing – original draft
      - Writing – review & editing
  - name          : "Savannah C. Lewis"
    affiliation   : "2"
    role:
      - Conceptualization
      - Data curation
      - Methodology
      - Project administration
      - Writing – original draft
      - Writing – review & editing
affiliation:

  - id            : "1"
    institution   : "Harrisburg University of Science and Technology"
  - id            : "2"
    institution   : "University of Alabama"
authornote: |
  Erin M. Buchanan is a Professor of Cognitive Analytics at Harrisburg University of Science and Technology. Savannah C. Lewis is a graduate student at the University of Alabama.

@@

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : papaja::apa6_docx
---

```{r setup, include = FALSE}
#knitr::opts_knit(echo = TRUE)
library(papaja)
library(knitr)
library(ggplot2)
library(treemapify)
library(countrycode)
library(rio)
library(maps)
library(dplyr)
library(tidyr)
library(MOTE)
library(MBESS)
library(patchwork)
library(flextable)
library(wordcloud2)
library(htmlwidgets)
library(webshot)
library(figpatch)

@@

***Institution and Geopolitical Region ***. We will use the affiliation ids and country to gather
information about the places of education and/or employment for authors.
Country will likely be binned into United Nation Region, Sub-Region,  or smaller clusters for
analyses.

@@

The total number of articles included in this analysis was `r total_num` including `r health_num` Health Sciences articles, `r physical_num` Physical Sciences articles, `r social_num` Social Sciences articles, and `r life_num` Life Sciences articles. Articles could be classified into multiple categories.

```{r}
ggplot(DF$pub_time_count %>% 
         filter(SubjectArea != "Multidisciplinary"), aes(Year, count, color = SubjectArea)) + 
  theme_classic() + 
  geom_point() + 
  scale_color_brewer(palette = "Spectral", name = "Subject Area") + 
  ylab("Number of Articles Per Year") + 
  xlab("Publication Year") + 
  theme(legend.position = "bottom")
```

@@

The number of distinct journals big team science articles were published in was `r journals` with `r health_journal` journals in Health Sciences, `r physical_journal` journals in Physical Sciences, `r social_journal` journals in Social Sciences, and `r life_journal` journals in Life Sciences. The descriptive statistics for the Source Normalized Impact per Paper is presented in Table X. For comparison, the SNIP descriptive statistics for all papers is shown in Table X.

Big-Team Science SNIP

```{r results = 'asis', include = TRUE}
flextable(
  DF$snip %>% 
    filter(`Subject Area` != "Multidisciplinary") %>% 
    mutate(M = apa_num(M), 
           SD = apa_num(SD), 
           Minimum = apa_num(Minimum), 
           Median = apa_num(Median), 
           Maximum = apa_num(Maximum))
)
```

All Journal Articles SNIP

```{r results = 'asis', include = TRUE}
flextable(
  DF$snip_all %>% 
    filter(`Subject Area` != "Multidisciplinary") %>% 
    mutate(M = apa_num(M), 
           SD = apa_num(SD), 
           Minimum = apa_num(Minimum), 
           Median = apa_num(Median), 
           Maximum = apa_num(Maximum))
)
```

@@

-   The totals of the number of articles published within the smaller
    subject area classifications. We will visualize these differences
    over time to determine if there is increasing interest in a specific
    subarea over time for each of the four larger subject area
    classifications.

#### REDO THIS WITH QUANTEDA ####

```{r}
#DF$pub_time_subject$ASJC <- factor(DF$pub_time_subject$ASJC)
pub_total <- DF$pub_time_subject %>% 
  group_by(SubjectArea, ASJC) %>% 
  summarize(count = sum(count), .groups = "keep") %>% 
  filter(SubjectArea != "Multidisciplinary") %>% 
  left_join(DF$ASJC_codes %>% select(Name, Code), by = c("ASJC" = "Code"))

health_cloud <- wordcloud2(pub_total %>% 
             filter(SubjectArea == "Health Sciences") %>% 
             ungroup() %>% 
             select(Name, count) %>% 
               arrange(desc(count)) %>% 
               slice_head(n = 20),
             minRotation = -pi/6, 
             maxRotation = -pi/6,
             rotateRatio = 0)

saveWidget(health_cloud, "tmp.html", selfcontained = F)
webshot("tmp.html", "figure/health_cloud.png", vwidth = 600, vheight = 600)

physical_cloud <- wordcloud2(pub_total %>% 
             filter(SubjectArea == "Physical Sciences") %>% 
             ungroup() %>% 
             select(Name, count) %>% 
               arrange(desc(count)) %>% 
               slice_head(n = 20),
             minRotation = -pi/6, 
             maxRotation = -pi/6,
             rotateRatio = 0, 
             size = 1.5)

saveWidget(physical_cloud, "tmp.html", selfcontained = F)
webshot("tmp.html", "figure/physical_cloud.png", vwidth = 600, vheight = 600)

life_cloud <- wordcloud2(pub_total %>% 
             filter(SubjectArea == "Life Sciences") %>% 
             ungroup() %>% 
             select(Name, count) %>% 
               arrange(desc(count)) %>% 
               slice_head(n = 20),
             minRotation = -pi/6, 
             maxRotation = -pi/6,
             rotateRatio = 0)

saveWidget(life_cloud, "tmp.html", selfcontained = F)
webshot("tmp.html", "figure/life_cloud.png", vwidth = 600, vheight = 600)

social_cloud <- wordcloud2(pub_total %>% 
             filter(SubjectArea == "Social Sciences") %>% 
             ungroup() %>% 
             select(Name, count) %>% 
               arrange(desc(count)) %>% 
               slice_head(n = 20),
             minRotation = -pi/6, 
             maxRotation = -pi/6,
             rotateRatio = 0, 
             size = .2)

saveWidget(social_cloud, "tmp.html", selfcontained = F)
webshot("tmp.html", "figure/social_cloud.png", vwidth = 600, vheight = 600)
```

```{r}
h <- fig("figure/health_cloud.png")
p <- fig("figure/physical_cloud.png") 
l <- fig("figure/life_cloud.png") 
s <- fig("figure/social_cloud.png")

h + ggtitle("Health Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
p + ggtitle("Physical Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
l + ggtitle("Life Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
s + ggtitle("Social Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  plot_layout(ncol = 2, 
              nrow = 2)
```

@@

```{r}
health_cloud <- wordcloud2(DF$keywords %>% 
             filter(SubjectArea == "Health Sciences") %>% 
             ungroup() %>% 
             select(keywords_nostop, count))

saveWidget(health_cloud, "tmp.html", selfcontained = F)
webshot("tmp.html", "figure/health_key.png", vwidth = 600, vheight = 600)

physical_cloud <- wordcloud2(DF$keywords %>% 
             filter(SubjectArea == "Physical Sciences") %>% 
             ungroup() %>% 
             select(keywords_nostop, count), 
             minSize = 20)

saveWidget(physical_cloud, "tmp.html", selfcontained = F)
webshot("tmp.html", "figure/physical_key.png", vwidth = 600, vheight = 600)

life_cloud <- wordcloud2(DF$keywords %>% 
             filter(SubjectArea == "Life Sciences") %>% 
             ungroup() %>% 
             select(keywords_nostop, count))

saveWidget(life_cloud, "tmp.html", selfcontained = F)
webshot("tmp.html", "figure/life_key.png", vwidth = 600, vheight = 600)

social_cloud <- wordcloud2(DF$keywords  %>% 
             filter(SubjectArea == "Social Sciences") %>% 
             ungroup() %>% 
             select(keywords_nostop, count))

saveWidget(social_cloud, "tmp.html", selfcontained = F)
webshot("tmp.html", "figure/social_key.png", vwidth = 600, vheight = 600)
```

```{r}
h <- fig("figure/health_key.png")
p <- fig("figure/physical_key.png") 
l <- fig("figure/life_key.png") 
s <- fig("figure/social_key.png")

h + ggtitle("Health Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
p + ggtitle("Physical Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
l + ggtitle("Life Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
s + ggtitle("Social Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  plot_layout(ncol = 2, 
              nrow = 2)
```

@@

##### FIX CAPTIONS #####

```{r}
avg_author_time <- 
  DF$author_time %>% 
  filter(SubjectArea != "Multidisciplinary") %>% 
  filter(Number_Papers >= 3) %>% 
  mutate(low = (Average_Num_Authors - as.numeric(SD_Num_Authors)), 
         high = (Average_Num_Authors + as.numeric(SD_Num_Authors)))

ggplot(avg_author_time, aes(Year, Med_Num_Authors)) + 
  theme_classic() + 
  geom_point(aes(size = Number_Papers)) + 
  geom_point(aes(Year, Average_Num_Authors, color = "red")) + 
  #geom_pointrange(aes(ymin = low, ymax = high)) + 
  facet_wrap(~SubjectArea) + 
  ylab("Average Number of Authors") + 
  xlab("Publication Year") + 
  theme(legend.position = "bottom")
```

@@

```{r}
ggplot(DF$career_time %>% 
         filter(SubjectArea != "Multidisciplinary"), 
       aes(Year, avg_career, color = sd_career)) +
  theme_classic() + 
  geom_point(aes(size = num_papers)) +
  facet_wrap(~SubjectArea) + 
  theme(legend.position = "bottom") + 
  ylab("Average Career Length") +
  xlab("Year of Publication")
```

@@

#### MOVE R2 to the right #####

```{r}
label <- c("Physical", "Social", "Health", "Life")
avg_b_values <- c(-0.531373, -0.437422, -0.460876, -0.604957)
avg_se_values <- c(0.030990, 0.058153, 0.009794, 0.026519)
sd_b_values <- c(-0.207000, -0.104549, -0.218675, -0.056843)
sd_se_values <- c(0.059698, 0.058153, 0.009794, 0.046915)
r2_values <- c(0.145118, 0.118772, 0.144584, 0.175747)
sample_size <- 13000

@@

@@

```{r}
DF$inst_time$normalized <- DF$inst_time$unique / DF$inst_time$total * 100

@@

    Figure out how messy this is for text processing requirements
    For each publication, plot of proportion of doctorates across time - if the number is going down, we are involving more diverse types of people (assuming that doctorates are "normal" academics/researchers)
    We will only perform this analysis if the proportion of information avaliable is over 50%.

+-----------+------+
|    degrees| count|
+-----------+------+
|       null|656440|
|         MD|  8190|
|        PhD|  3879|
|    MD, PhD|  1267|
|       M.D.|  1002|
|        Dr.|   490|
|        MSc|   461|
|        MPH|   368|
| Prof., PhD|   349|
|      Ph.D.|   348|
|         MS|   330|
|     MD PhD|   285|
|        MD.|   279|
|   Prof. MD|   266|
|  Prof. PhD|   239|
|         BS|   232|
|       Prof|   220|
|         BA|   196|
|M.D., Ph.D.|   191|
|    MD, MPH|   158|
+-----------+------+

@@

```{r}
pub_types <- bind_rows(
  DF$pub_types %>% mutate(type = "Big Team"), 
  DF$normal_pub_type %>% mutate(type = "Normal")
) %>% 
  filter(publication_type == "ar" | publication_type == "pp" | 
           publication_type == "dp")

ggplot(pub_types, aes(type, count, fill = publication_type)) + 
    geom_bar(position="fill", stat="identity", color = "black") + 
  theme_classic() +  
  xlab("Author Type") + 
  ylab("Percent of Paper Types") + 
  theme(legend.position = "right")

@@

# can probably figure out how to combine these feasibly to make it readable

# ab Abstract Report, ar Article, ip Article in Press, bk Book, bz Business Article, ch Book Chapter, cp Conference Paper, cr Conference Review, dp Data paper, ed Editorial, er Erratum, le Letter, no Note, pp Preprint, pr Press Release, rp Report, re Review, sh Survey, tb Retracted.

@@

```{r}
label <- c("Physical", "Social", "Health", "Life")
avg_b_values <- c(-0.004420, -0.335536, -0.235551, -0.430599)
avg_se_values <- c(0.022715, 0.179536, 0.028158, 0.037807)
sd_b_values <- c(-0.105746, 0.130796, -0.006692, 0.133215)
sd_se_values <- c(0.034058, 0.186924, 0.026612, 0.034255)
r2_values <- c(0.009554, 0.021558, 0.035782, 0.054081)
sample_size <- 13000

@@

# make a map on a continuous scale
ggplot(DF$geo_country) +
  geom_map(aes(map_id = affiliation_tag_country, fill = count), map = world_map) +
  geom_polygon(data = world_map, 
               aes(x = long, y = lat, group = group), 
               colour = 'black', fill = NA) + 
  theme_void() + 
  scale_fill_distiller(name = "Sample Size",
                       palette = "Greys",
                       direction = 1,
                       na.value = "white")

ggsave("figure/continuous_country.png")

@@

bin_country

ggsave("figure/binned_country.png", bin_country)

@@

tree <- ggplot(DF$geo_country, aes(area = count, fill = count_binned,
               label = affiliation_tag_country, subgroup = un_region_sub)) +
  geom_treemap() +
  geom_treemap_subgroup_border(colour = "white", size = 5) +
  # geom_treemap_subgroup_text(place = "top", grow = TRUE,
  #                            alpha = 0.25, colour = "black",
  #                            fontface = "italic") +
  geom_treemap_text(colour = "black", place = "centre",
                    size = 15, grow = FALSE) +  
  # scale_fill_manual(name = "Sample Size",
  #                   values = c("#c8c8c8", "#969696", "#646464", "#323232", "black")) 
  scale_fill_brewer(name = "Sample Size", palette = "Spectral")
  # scale_fill_gradient(name = "Sample Size",
  #                     low = "#c8c8c8", 
  #                     high = "#323232")

tree

ggsave("figure/treemap.png", tree)
```

```{r geo-map-all}
# make a map on a continuous scale
ggplot(DF$geo_country) +
  geom_map(aes(map_id = affiliation_tag_country, fill = count_all), map = world_map) +
  geom_polygon(data = world_map, 
               aes(x = long, y = lat, group = group), 
               colour = 'black', fill = NA) + 
  theme_void() + 
  scale_fill_distiller(name = "Sample Size",
                       palette = "Greys",
                       direction = 1,
                       na.value = "white")

ggsave("figure/continuous_country_all.png")

# maybe try binning
DF$geo_country$count_binned_all <- if_else(
  DF$geo_country$count_all >= 10000, "10,000+", 
  if_else(
    DF$geo_country$count_all < 10000 & DF$geo_country$count_all >= 5000, "5,000-9,999",
    if_else(
      DF$geo_country$count_all < 5000 & DF$geo_country$count_all >= 1000, "1,000-4,999",
      if_else(
        DF$geo_country$count_all < 1000 & DF$geo_country$count_all >= 100, "100-999",
        "< 100"
      )
    )
  )
)

@@

bin_country_all

ggsave("figure/binned_country_all.png", bin_country_all)

tree_all <- ggplot(DF$geo_country, aes(area = count_all, fill = count_binned_all,
               label = affiliation_tag_country, subgroup = un_region_sub)) +
  geom_treemap() +
  geom_treemap_subgroup_border(colour = "white", size = 5) +
  # geom_treemap_subgroup_text(place = "top", grow = TRUE,
  #                            alpha = 0.25, colour = "black",
  #                            fontface = "italic") +
  geom_treemap_text(colour = "black", place = "centre",
                    size = 15, grow = FALSE) +  
  # scale_fill_manual(name = "Sample Size",
  #                   values = c("#c8c8c8", "#969696", "#646464", "#323232", "black")) 
  scale_fill_brewer(name = "Sample Size", palette = "Spectral")
  # scale_fill_gradient(name = "Sample Size",
  #                     low = "#c8c8c8", 
  #                     high = "#323232")

tree_all

ggsave("figure/treemap_all.png", tree_all)
```

#### four panel plot with tree and country next to each other ####

>>>>

---
title             : "Who does big team science?"
shorttitle        : "Big Team Science"
author: 
  - name          : "Erin M. Buchanan"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "326 Market St., Harrisburg, PA 17101"
    email         : "ebuchanan@harrisburgu.edu"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Data curation
      - Formal Analysis
      - Methodology
      - Project administration
      - Visualization
      - Writing – original draft
      - Writing – review & editing
  - name          : "Savannah C. Lewis"
    affiliation   : "2"
    role:
      - Conceptualization
      - Data curation
      - Methodology
      - Project administration
      - Writing – original draft
      - Writing – review & editing
affiliation:
  - id            : "1"
    institution   : "Harrisburg University of Science and Technology"
  - id            : "2"
    institution   : "University of Alabama"
authornote: |
  Erin M. Buchanan is a Professor of Cognitive Analytics at Harrisburg University of Science and Technology. Savannah C. Lewis is a graduate student at the University of Alabama.

@@

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
knitr::opts_knit$set(echo = FALSE, warning = FALSE, message = FALSE, include = FALSE, error = FALSE)
library(papaja)
library(knitr)
library(ggplot2)
library(treemapify)
library(countrycode)
library(rio)
library(maps)
library(dplyr)
library(tidyr)
library(MOTE)
library(MBESS)
library(patchwork)
library(ggplot2)
library(ggwordcloud)
library(figpatch)

@@

***Institution and Geopolitical Region*** . We will use the affiliation
ids and country to gather information about the places of education
and/or employment for authors. Country will likely be binned into United Nation Region, Sub-Region, or smaller clusters for analyses.

@@

*Number of articles*. The total number of articles included in this analysis was `r total_num` including `r health_num` Health Sciences articles, `r physical_num`
Physical Sciences articles, `r social_num` Social Sciences articles, and
`r life_num` Life Sciences articles. Articles could be classified into
multiple categories. Figure X shows the number of articles published across time for each of the four large subject areas.

```{r fig-pub-time, include = TRUE, fig.cap="Number of big-team science publications separated by four large subject areas across years."}
ggplot(DF$pub_time_count %>% 
         filter(SubjectArea != "Multidisciplinary"), aes(Year, count, color = SubjectArea)) + 
  theme_classic() + 
  geom_point() + 
  scale_color_brewer(palette = "Spectral", name = "Subject Area") + 
  ylab("Number of Articles Per Year") + 
  xlab("Publication Year") + 
  theme(legend.position = "bottom")
```

@@

*Number of journals*. The number of distinct journals big team science articles were published
in was `r journals` with `r health_journal` journals in Health Sciences,
`r physical_journal` journals in Physical Sciences, `r social_journal`
journals in Social Sciences, and `r life_journal` journals in Life
Sciences. The descriptive statistics for the Source Normalized Impact
per Paper is presented in Table X. For comparison, the SNIP descriptive
statistics for all papers is shown in Table X.

```{r tab-snip, results = 'asis', include = TRUE}
apa_table(
  DF$snip %>% 
    filter(`Subject Area` != "Multidisciplinary") %>% 
    mutate(M = apa_num(M), 
           SD = apa_num(SD), 
           Minimum = apa_num(Minimum), 
           Median = apa_num(Median), 
           Maximum = apa_num(Maximum)), 
  caption = "Big-Team Science SNIP Values")
```

```{r results = 'asis', include = TRUE}
apa_table(
  DF$snip_all %>% 
    filter(`Subject Area` != "Multidisciplinary") %>% 
    mutate(M = apa_num(M), 
           SD = apa_num(SD), 
           Minimum = apa_num(Minimum), 
           Median = apa_num(Median), 
           Maximum = apa_num(Maximum)),
  caption = "All Journal Articles SNIP Values")
```

@@

-   The totals of the number of articles published within the smaller
    subject area classifications. We will visualize these differences to show the areas of interest for each of the four large subject areas.

```{r eval = FALSE, warning = FALSE, echo = FALSE, message = FALSE}
### NOTE YOU WILL NEED TO RUN THIS ###
#DF$pub_time_subject$ASJC <- factor(DF$pub_time_subject$ASJC)
pub_total <- DF$pub_time_subject %>% 
  group_by(SubjectArea, ASJC) %>% 
  summarize(Count_Size = sum(count), .groups = "keep") %>% 
  filter(SubjectArea != "Multidisciplinary") %>% 
  left_join(DF$ASJC_codes %>% select(Name, Code), by = c("ASJC" = "Code"))

# health

health_cloud <- pub_total %>% 
  filter(SubjectArea == "Health Sciences") %>% 
  ungroup() %>%
  arrange(desc(Count_Size)) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

ggsave("figure/health_cloud.png", dpi = 300, width = 8,
       height = 4, units = "in")

physical_cloud <- pub_total %>% 
  filter(SubjectArea == "Physical Sciences") %>% 
  ungroup() %>%
  arrange(desc(Count_Size)) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

ggsave("figure/physical_cloud.png", dpi = 300, width = 8,
       height = 4, units = "in")

life_cloud <- pub_total %>% 
  filter(SubjectArea == "Life Sciences") %>% 
  ungroup() %>%
  arrange(desc(Count_Size)) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

ggsave("figure/life_cloud.png", dpi = 300, width = 8,
       height = 4, units = "in")

social_cloud <- pub_total %>% 
  filter(SubjectArea == "Social Sciences") %>% 
  ungroup() %>%
  arrange(desc(Count_Size)) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

ggsave("figure/social_cloud.png", dpi = 300, width = 8,
       height = 4, units = "in")
```

```{r fig-clouds, include = TRUE, fig.cap = "Journal Areas for Big-Team Science Publications by Subject Area"}

health_cloud <- fig("figure/health_cloud.png")
physical_cloud <- fig("figure/physical_cloud.png") 
life_cloud <- fig("figure/life_cloud.png") 
social_cloud <- fig("figure/social_cloud.png")

health_cloud + ggtitle("Health Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
physical_cloud + ggtitle("Physical Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
life_cloud + ggtitle("Life Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
social_cloud + ggtitle("Social Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  plot_layout(ncol = 2, 
              nrow = 2)
```

@@

```{r eval = FALSE, warning = FALSE, echo = FALSE, message = FALSE}
### NOTE YOU WILL NEED TO RERUN THIS ###
health_cloud <- DF$keywords %>% 
   filter(SubjectArea == "Health Sciences") %>% 
   ungroup() %>% 
   select(keywords_nostop, count) %>% 
  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

ggsave("figure/health_key.png", dpi = 300, width = 8,
       height = 4, units = "in")

physical_cloud <- DF$keywords %>% 
   filter(SubjectArea == "Physical Sciences") %>% 
   ungroup() %>% 
   select(keywords_nostop, count) %>% 
  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

ggsave("figure/physical_key.png", dpi = 300, width = 8,
       height = 4, units = "in")

life_cloud <- DF$keywords %>% 
   filter(SubjectArea == "Life Sciences") %>% 
   ungroup() %>% 
   select(keywords_nostop, count) %>% 
  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

ggsave("figure/life_key.png", dpi = 300, width = 8,
       height = 4, units = "in")

social_cloud <- DF$keywords %>% 
   filter(SubjectArea == "Social Sciences") %>% 
   ungroup() %>% 
   select(keywords_nostop, count) %>% 
  dplyr::rename(Count_Size = count, Name = keywords_nostop) %>% 
  ggplot() + 
  geom_text_wordcloud_area(aes(label = Name, size = Count_Size), area_corr_power = TRUE, rm_outside = TRUE, shape = "square", perc_step = .001, grid_margin = .01) + 
  theme_minimal() + 
  scale_size_area(max_size = 15)

ggsave("figure/social_key.png", dpi = 300, width = 8,
       height = 4, units = "in")
```

```{r fig-keywords, include = TRUE, fig.cap="Keyword Analysis for Each of the Four Subject Areas."}
health_key <- fig("figure/health_key.png")
physical_key <- fig("figure/physical_key.png") 
life_key <- fig("figure/life_key.png") 
social_key <- fig("figure/social_key.png")

health_key + ggtitle("Health Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
physical_key + ggtitle("Physical Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
life_key + ggtitle("Life Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
social_key + ggtitle("Social Sciences") + 
  theme(plot.title = element_text(hjust = 0.5)) +
  plot_layout(ncol = 2, 
              nrow = 2)
```

@@

```{r fig-author-year, include = TRUE, fig.cap="Number of authors included on big-team science papers per year by subject area. Colored dots indicate the mean number of authors, while the black dots represent the median number of authors. The size of the black dots indicate the number of papers in that year."}
avg_author_time <- 
  DF$author_time %>% 
  filter(SubjectArea != "Multidisciplinary") %>% 
  filter(Number_Papers >= 3) %>% 
  mutate(low = (Average_Num_Authors - as.numeric(SD_Num_Authors)), 
         high = (Average_Num_Authors + as.numeric(SD_Num_Authors)))

ggplot(avg_author_time, aes(Year, Med_Num_Authors)) + 
  theme_classic() + 
  geom_point(aes(size = Number_Papers)) + 
  geom_point(aes(Year, Average_Num_Authors, color = "red")) + 
  #geom_pointrange(aes(ymin = low, ymax = high)) + 
  facet_wrap(~SubjectArea) + 
  ylab("Average Number of Authors") + 
  xlab("Publication Year") + 
  theme(legend.position = "bottom") + 
  guides(color = "none") + 
  scale_size_continuous(name = "Number Papers")
```

@@

```{r fig-career, include = TRUE, fig.cap = "Average career length for big-team science authors. Larger dots indicate more papers for each estimation. Lighter colored dots mean less variability in author career length, while darker dots mean more variability in career length."}
ggplot(DF$career_time %>% 
         filter(SubjectArea != "Multidisciplinary"), 
       aes(Year, avg_career, color = sd_career)) +
  theme_classic() + 
  geom_point(aes(size = num_papers)) +
  facet_wrap(~SubjectArea) + 
  theme(legend.position = "bottom") + 
  ylab("Average Career Length") +
  xlab("Year of Publication") + 
  guides(color = "none") + 
  scale_size_continuous(name = "Number Papers")
```

@@

```{r fig-career-results, include = TRUE, fig.cap = "Coefficient values for the average career length, variance in career length, and the effect size for each model predicting year of publication."}
label <- c("Physical", "Social", "Health", "Life")
avg_b_values <- c(-0.531373, -0.437422, -0.460876, -0.604957)
avg_se_values <- c(0.030990, 0.058153, 0.009794, 0.026519)
sd_b_values <- c(-0.207000, -0.104549, -0.218675, -0.056843)
sd_se_values <- c(0.059698, 0.058153, 0.009794, 0.046915)
r2_values <- c(0.145118, 0.118772, 0.144584, 0.175747)
sample_size <- 13000

@@

graph_data$type <- factor(
  graph_data$type, 
  levels = c("M Coefficient", "SD Coefficient", "Effect Size")
)

@@

```{r fig-inst, include = TRUE, fig.cap="Number of unique institutions involved in big-team science papers across decades."}
DF$inst_time$normalized <- DF$inst_time$unique / DF$inst_time$total * 100

@@

- For each publication, plot of proportion of doctorates across time - if the number is going down, we are involving more diverse types of people (assuming that doctorates are "normal" academics/researchers)
- We will only perform this analysis if the proportion of information avaliable is over 50%.

+--------+--------+
| d      | count  |
| egrees |        |
+--------+--------+
| ``` CE | 656440 |
| F7FA46 | 8190   |
|        | 3879   |
|   null | 1267   |
|        | 1002   |
|     MD | 490    |
|        | 461    |
|    PhD | 368    |
| M      | 349    |
| D, PhD | 348    |
|        | 330    |
|   M.D. | 285    |
|        | 279    |
|    Dr. | 266    |
|        | 239    |
|    MSc | 232    |
|        | 220    |
|    MPH | 196    |
| ```    | 191    |
|        | 158    |
| Prof., |        |
| PhD    |        |
| Ph.D.  |        |
| MS MD  |        |
| PhD    |        |
| MD.    |        |
| Prof.  |        |
| MD     |        |
| Prof.  |        |
| PhD BS |        |
| Prof   |        |
| BA     |        |
| M.D.,  |        |
| Ph.D.  |        |
| MD,    |        |
| MPH    |        |
+--------+--------+

@@

```{r fig-pub-types, include = TRUE, fig.cap = "Types of publications for big-team science and all authors."}
pub_types <- bind_rows(
  DF$pub_types %>% mutate(type = "Big Team"), 
  DF$normal_pub_type %>% mutate(type = "Normal")
) %>% 
  filter(publication_type == "ar" | publication_type == "pp" | 
           publication_type == "dp")

ggplot(pub_types, aes(type, count, fill = publication_type)) + 
    geom_bar(position="fill", stat="identity", color = "black") + 
  theme_classic() +  
  xlab("Author Type") + 
  ylab("Percent of Paper Types") + 
  theme(legend.position = "bottom") + 
  scale_fill_discrete(name = "Publication Type", labels = c("Article", "Data Paper", "Pre-Print"))

@@

@@

```{r fig-pub-results, include = TRUE, fig.cap = "Coefficient values for the publication totals, variance in publication totals, and the effect size for each model predicting year of publication."}
label <- c("Physical", "Social", "Health", "Life")
avg_b_values <- c(-0.004420, -0.335536, -0.235551, -0.430599)
avg_se_values <- c(0.022715, 0.179536, 0.028158, 0.037807)
sd_b_values <- c(-0.105746, 0.130796, -0.006692, 0.133215)
sd_se_values <- c(0.034058, 0.186924, 0.026612, 0.034255)
r2_values <- c(0.009554, 0.021558, 0.035782, 0.054081)
sample_size <- 13000

@@

@@

@@

tree <- ggplot(DF$geo_country, aes(area = count, fill = count_binned,
               label = affiliation_tag_country, subgroup = un_region_sub)) +
  geom_treemap() +
  geom_treemap_subgroup_border(colour = "white", size = 5) +
  # geom_treemap_subgroup_text(place = "top", grow = TRUE,
  #                            alpha = 0.25, colour = "black",
  #                            fontface = "italic") +
  geom_treemap_text(colour = "black", place = "centre",
                    size = 15, grow = FALSE) +  
  # scale_fill_manual(name = "Sample Size",
  #                   values = c("#c8c8c8", "#969696", "#646464", "#323232", "black")) 
  scale_fill_brewer(name = "Sample Size", palette = "Spectral")
  # scale_fill_gradient(name = "Sample Size",
  #                     low = "#c8c8c8", 
  #                     high = "#323232") 
```

```{r geo-map-all}
# maybe try binning
DF$geo_country$count_binned_all <- if_else(
  DF$geo_country$count_all >= 10000, "10,000+", 
  if_else(
    DF$geo_country$count_all < 10000 & DF$geo_country$count_all >= 5000, "5,000-9,999",
    if_else(
      DF$geo_country$count_all < 5000 & DF$geo_country$count_all >= 1000, "1,000-4,999",
      if_else(
        DF$geo_country$count_all < 1000 & DF$geo_country$count_all >= 100, "100-999",
        "< 100"
      )
    )
  )
)

@@

tree_all <- ggplot(DF$geo_country, aes(area = count_all, fill = count_binned_all,
               label = affiliation_tag_country, subgroup = un_region_sub)) +
  geom_treemap() +
  geom_treemap_subgroup_border(colour = "white", size = 5) +
  # geom_treemap_subgroup_text(place = "top", grow = TRUE,
  #                            alpha = 0.25, colour = "black",
  #                            fontface = "italic") +
  geom_treemap_text(colour = "black", place = "centre",
                    size = 15, grow = FALSE) +  
  # scale_fill_manual(name = "Sample Size",
  #                   values = c("#c8c8c8", "#969696", "#646464", "#323232", "black")) 
  scale_fill_brewer(name = "Sample Size", palette = "Spectral")
  # scale_fill_gradient(name = "Sample Size",
  #                     low = "#c8c8c8", 
  #                     high = "#323232") 
```
